
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 3.  Working with Data Frame. Base R Style"
---

***Note*:** *This assignment practices working with Data Frame using Base R.*

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment3.Rmd)) in Rstudio. 

- Right under each question, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas under Assignment 3. 

-------

Problems
-------
 \

1. Create the following data frame

| Rank 	| Age 	| Name  	|
|:------	|:-----	|:-------	|
| 0    	| 28  	| Tom   	|
| 1    	| 34  	| Jack  	|
| 2    	| 29  	| Steve 	|
| 3    	| 42  	| Ricky 	|

```{r}
mdf = data.frame(Rank = c(0, 1, 2, 3),
                Age = c(28, 34, 29, 42),
                Name = c('Tom', 'Jack', 'Steve', 'Ricky'))
```


2. Use `read.csv` to import the Covid19 Vaccination data from WHO: [link](https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv).

```{r}
df = read.csv('https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv')
```


2. Show the names of the variables in the data

```{r}
names(df)
```


3. How many columns and rows the data have? 

```{r}
str(df)
```


4. How many missing values are there?  Show the missing values by columns.  What variable has the most number of missing values?

```{r}
colSums(is.na(df))
```


5. What is the class of the `date` column. Change the `date` columns to `date` type using the `as.Date` function. Show the new class of the `date` column. 

```{r}
class(df$date)
df$date = as.Date(df$date)
class(df$date)
```


6. Capitalize the names of all the variables

```{r}
names(df)[1] <- 'Date'
names(df)[2] <- 'State'
names(df)[3] <- 'Fips'
names(df)[4] <- 'Cases'
names(df)[5] <- 'Deaths'
```


7. Find the average number of cases per day. Find the maximum cases a day.

```{r}
mean(df$Cases, na.rm=TRUE)
max(df$Cases, na.rm=TRUE)
```


8. How many states are there in the data?  

```{r}
table(df$State)
```


9. Create a new variable `weekdays` to store the weekday for each rows. 

```{r}
library(dplyr)
df$weekdays <- weekdays(as.Date(df$Date))
```


10. Create the categorical variable `death2` variable taking the values as follows

- `has_death` if there is a death that day
-  `no_death` if there is no death that day

```{r}
df$death2 = case_when(df$Deaths==0 ~ 'no_death', 
                            TRUE ~ 'has_death')
```


Find the frequency and relative frequency of `no_death` and `has_death`. 

```{r}
table(df$death2)
prop.table(table(df$death2))
```


11. Find the first quartile (Q1), second quartile (Q2) and and third quartile (Q3) of the variable `death`. (Hint:  Use the `summary` function)

```{r}
summary(df$Deaths)
```


12. Create the categorical variable `death3` variable taking the values as follows

- `low_death` if the number of deaths smaller than the 25 percentile (Q1)

- `mid_death` if the number of deaths from Q1 to Q3

- `high_death` if the number of deaths greater than Q3

```{r}
df$death3 = case_when(df$Deaths<1171 ~ 'low_death',
                             df$Deaths<5035 ~ 'mid_death',
                             TRUE~'high_death')
```


13. Find the average cases in Rhode Island in 2021

```{r}
library(lubridate)
df1 <- df[(df$State=='Rhode Island') & (df$Date>='2021-01-01') & (df$Date<='2022-01-01'),]
mean(df1$Cases, na.rm = TRUE)
```


14. Find the median cases by weekdays in Rhode Island in 2021 

```{r}
df2 <- df[(df$State=='Rhode Island') & (df$Date>='2021-01-01') & (df$Date<='2022-01-01'),]
by(df2$Cases,df2$weekdays, median)
```


15. Compare the median cases in Rhode Island in June, July, August and September in 2021. 

```{r}
df$month <- month(df$Date, label = TRUE)
df3 <- df[(df$State=='Rhode Island') & (df$Date>='2021-06-01') & (df$Date<'2021-10-01'),]
by(df3$Cases, df3$month, median)
```


16.  Find your own dataset, import it and implement the following functions on the data

- head
- str
- names
- mean, min, max
- table
- is.na
- colSums
- class
- cor
- by
- ifelse
- case_when

```{r}
dft = read.csv('https://bryantstats.github.io/math421/data/titanic.csv')
head(dft)
```
```{r}
str(dft)
```
```{r}
names(dft)
```
```{r}
summary(dft)
```
```{r}
table(dft$Survived)
```
```{r}
colSums(is.na(dft))
```
```{r}
class(dft$Survived)
```
```{r}
cor(dft$Pclass, dft$Survived)
```
```{r}
dft1 <- dft[dft$Sex=='female' & dft$Survived == 1,]
by(dft1$Age,dft1$Pclass, mean, na.rm = TRUE)


```
```{r}
dft$Adult <- ifelse(dft$Age>=18.00, 
                        'Yes','No')
```

```{r}
dft$specificAge <- case_when(dft$Age<13 ~ 'kid',
                             dft$Age<20 ~ 'teenager',
                             TRUE~'adult')
table(dft$specificAge)
```

17.  In the dataset in #16, practice the follows.  You can reuse the code of 16. 

- Create a categorical variable from a continuous variable
- From one categorical variable, create a new categorical variable with fewer categories

```{r}
dft$Price <- case_when(dft$Fare<25 ~ 'lowPrice',
                             dft$Fare<100 ~ 'midPrice',
                             TRUE~'highPrice')
table(dft$Price)
```
```{r}
dft$firstClass <- case_when(dft$Pclass %in% c(1) ~ 'Yes',
                       dft$Pclass %in% c(2,3) ~ 'No')
```


If you do not have a data, you can use [the titanic dataset](https://www.kaggle.com/competitions/titanic/overview), which can be downloaded at [this link](../data/titanic.csv)
