
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 7 - Extra Credits: Practice dplyr and ggplot2"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment7_extra_credits.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas



```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```


-------

1. Import the data at https://bryantstats.github.io/math421/data/ds_salaries.csv

    The data description can be found at https://www.kaggle.com/datasets/saurabhshahane/data-science-jobs-salaries
    
```{r}
library(tidyverse)
df <- read_csv('https://bryantstats.github.io/math421/data/ds_salaries.csv')
```
    

2. Is there any column that contains NAs?

```{r}
colSums(is.na(df))
```
There are no NA in any column

3. What is the most frequent job title in the data?  

```{r}
df %>% 
  count(job_title) %>% 
  arrange(-n)
```
Data Scientist is the most frequent job title

4. Find the average salary data of the three most frequent job titles in the data. 

```{r}
df %>%
  group_by(job_title) %>% 
  summarise(mean_salary = mean(salary, na.rm=TRUE)) 
```
Data Scientist = $508,347.20
Data Engineer = $179,210.55	
Data Analyst = $96,604.96	

5. What is the job title that have the highest average salary?

```{r}
df %>%
  group_by(job_title) %>% 
  summarise(mean_salary = mean(salary, na.rm=TRUE)) %>% 
  arrange(-mean_salary)
```
Head of Machine Learning has highest average salary.

6. Which country gives the highest salary on average? 

```{r}
df %>% 
  group_by(company_location) %>% 
  summarise(mean_salary = mean(salary, na.rm=TRUE)) %>% 
  arrange(-mean_salary)
```
It says that CL gives the highest salary on average.

7. Plot five meaningful plots. All plots should have title, caption, and appropriate labels.

```{r}
df %>% ggplot()+ 
  geom_bar(mapping=aes(x= company_size, fill =company_location), 
           position = 'dodge') +
  labs(x='Company Size', 
       y = 'Count of Companies',  
       title = 'Copmany Size based on Location', 
       caption = 'In general, countries in the US have a lot more companies.')
```
```{r}
df %>% ggplot()+ 
  geom_bar(mapping=aes(x=experience_level, fill=employment_type), 
           position = 'fill') +
  labs(x='Experience Level', 
       y = 'Individuals Employment Type',  
       title = 'Employment Type with Experience Level', 
       caption = 'The majority of the employment type no matter the experience level is FT.')
```

```{r}
df %>% 
  ggplot()+
  geom_point(mapping = aes(x = work_year, y = salary, color = salary_currency)) +
  labs(x='Year of Work', 
       y = 'Salary',  
       title = 'Salary Currency used compared to Salary', 
       caption = 'One salary currency used that is very high is CLP in 2021')
```
```{r}
df %>% ggplot()+ 
  geom_bar(mapping=aes(x=employment_type, fill=salary_currency), 
           position = 'dodge') +
  labs(x='Employment Type', 
       y = 'Count of Employees',  
       title = 'Salary Currency with Employment Type', 
       caption = 'The employment type FT has the most diverse selection of salary currency.')
```
```{r}
df %>% 
  filter(salary_currency == "USD", company_location == 'US') %>% 
  ggplot()+
  geom_point(mapping = aes(x = work_year, y = salary_in_usd)) +
  labs(x='Year of Work', 
       y = 'Salary in USD',  
       title = 'Salary in USD in the USA', 
       caption = 'In 2020, the salaries are much less compared to 2021 and 2022')
```

