
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 16: Writing a function - Loop"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment16.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

1. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: a data frame with all the missing of numeric variables replaced by the associated means.

Hint: [Similar function](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#28)

```{r}
library(tidyverse)
df <- read_csv('titanic.csv')
numeric_impute_mean <- function(d) {
  for (i in 1:ncol(d)) {
    if (is.numeric(d[[i]])) {
      d[[i]] <- ifelse(is.na(d[[i]]), mean(d[[i]], na.rm = TRUE), d[[i]])
    }
  }
  return(d)
}

df <- read_csv('titanic.csv')
colSums(is.na(df))
d1 <- numeric_impute_mean(df)
colSums(is.na(d1))
```


-------

2. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: a data frame with all the missing of variables replaced by the associated means (for numeric variables) or modes (for non-numeric variables).

Hint: Use If-statement to combine the function in Problem 1 and the function in [this example](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#28)

```{r}
calculate_mode <- function(x) {
  unique_values <- unique(x)
  tab <- table(x)
  modes <- unique_values[tab == max(tab)]
  return(modes)
}

impute_mean_mode <- function(d) {
  for (i in 1:ncol(d)) {
    if (is.numeric(d[[i]])) {
      d[[i]] <- ifelse(is.na(d[[i]]), mean(d[[i]], na.rm = TRUE), d[[i]])
    } else {
      d[[i]] <- ifelse(is.na(d[[i]]), calculate_mode(d[[i]]), d[[i]])
    }
  }
  return(d)
}

colSums(is.na(df))
d2 <- impute_mean_mode(df)
colSums(is.na(d2))
```



-------

3. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: Bar plots of all non-numeric variables

Hint: [Similar function](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#33)

```{r}
bar_plots_non_numeric <- function(d) {
  library(ggplot2)
  
  non_numeric_columns <- d %>%
    select_if(~ !is.numeric(.)) %>%
    names()
  
  for (col in non_numeric_columns) {
    plot_data <- d %>%
      count({{ col }}) %>%
      ggplot(aes(x = {{ col }}, y = n, fill = as.factor({{ col }}))) +
      geom_bar(stat = "identity") +
      labs(title = paste("Bar Plot of", col),
           x = col,
           y = "Count") +
      theme_minimal()
    
    print(plot_data)
  }
}

bar_plots_non_numeric(df)
```


-------

4. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: all possible the bar plots of a non-numeric variable filled by a non-numeric variable.

Hint: [Similar function](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#40)

```{r}
bar_plots_filled_by_non_numeric <- function(d) {

  non_numeric_columns <- d %>%
    select_if(~ !is.numeric(.)) %>%
    names()
  
  for (i in 1:(length(non_numeric_columns) - 1)) {
    for (j in (i + 1):length(non_numeric_columns)) {
      col1 <- non_numeric_columns[i]
      col2 <- non_numeric_columns[j]
      
      plot_data <- d %>%
        ggplot(aes(x = !!sym(col1), fill = !!sym(col2))) +
        geom_bar() +
        labs(title = paste("Bar Plot of", col1, "filled by", col2),
             x = col1,
             y = "Count",
             fill = col2) +
        theme_minimal()
      
      print(plot_data)
    }
  }
}

bar_plots_filled_by_non_numeric(df)
```


-------

5. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: 

  - all possible the bar plots of a non-numeric variable filled by a non-numeric variable.
  
  - all possible the density plots of a numeric variable colored by a non-numeric variable
  
  - all possible the scatter plots.

Hint: Combine [this function](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#37), [this function](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#40), and the function in Question 4. One way to combine is creating a new function, `quick_plot`, and call these three functions within `quick_plot`. 

```{r}
scatter_plot <- function(d) {
  l <- length(d)
  for (i in 1:(l - 1))
    for (j in (i + 1):l) {
      if (is.numeric(d[[i]]) & is.numeric(d[[j]])) {
        print(ggplot(d, aes(x = d[[i]], y = d[[j]])) +
                geom_point() +
                labs(x = names(d)[i], y = names(d)[j]))
      }
    }
}

density_plot2 <- function(d) {
  l <- length(d)
  for (i in 1:(l - 1))
    for (j in (i + 1):l) {
      if (is.numeric(d[[i]]) & (!is.numeric(d[[j]]))) {
        print(ggplot(d, aes(x = d[[i]], color = d[[j]])) +
                geom_density() +
                labs(x = names(d)[i], color = names(d)[j]))
      }
    }
}

bar_plots_filled_by_non_numeric <- function(d) {
  non_numeric_columns <- d %>%
    select_if(~ !is.numeric(.)) %>%
    names()
  
  for (i in 1:(length(non_numeric_columns) - 1)) {
    for (j in (i + 1):length(non_numeric_columns)) {
      col1 <- non_numeric_columns[i]
      col2 <- non_numeric_columns[j]
      
      plot_data <- d %>%
        ggplot(aes(x = !!sym(col1), fill = !!sym(col2))) +
        geom_bar() +
        labs(title = paste("Bar Plot of", col1, "filled by", col2),
             x = col1,
             y = "Count",
             fill = col2) +
        theme_minimal()
      
      print(plot_data)
    }
  }
}

quick_plot <- function(d) {
  scatter_plot(d)
  density_plot2(d)
  bar_plots_filled_by_non_numeric(d)
}

quick_plot(df)
```


