
---
output: # rmarkdown::github_document
  html_document:
    theme: cerulean
    toc: true
  pdf_document: default
  word_document: default
title: "Assignment 5: Handle Missing Values"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment5.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

**The data:** 

This assignment works with the Adult Census Data that can be downloaded at [this link.](https://bryantstats.github.io/math421/data/adult_census_missing.csv)

-------

**Questions**

1. Use `read_csv` to import the data.  Show the number of NAs for each columns.

```{r}
library(tidyverse)
dft = read_csv('https://bryantstats.github.io/math421/data/adult_census_missing.csv')
colSums(is.na(dft))
```


2. Using function `aggr` the VIM package to plot the number of NAs for each column. 

```{r}
#install.packages("VIM")
library(VIM)
aggr(dft)
```


3. Find other forms of missing values. Hint: You can use the `table` function to check if there are suspicious categories (Unknown, for example) in a variable. What all other forms of missing values shown in the data. 

```{r}
colSums(is.na(dft))
```


```{r}
table(dft$workclass)
table(dft$education)
table(dft$age)
table(dft$fnlwgt)
table(dft$education.num)
table(dft$marital.status)
table(dft$occupation)
table(dft$relationship)
table(dft$race)
table(dft$sex)
table(dft$capital.gain)
table(dft$capital.loss)
table(dft$hours.per.week)
table(dft$native.country)
table(dft$income)
```


4. Replace all the forms of missing values found to NA

```{r}

dft2 <- replace(dft, dft == 'Unknown' |
                  dft == 'Not Known' |
                  dft == '?', NA)

colSums(is.na(dft2))

```


5. Replot the number of NAs for each column. 

```{r}
aggr(dft2)
```

6. Approach 1 to handle NAs: remove all rows that have any NAs. Save the dataset after removing as a different data. The original data is unchanged (still have NAs).  How many rows left after removing?

```{r}
str(dft2)
dft3 = drop_na(dft2)
str(dft3)
```

7. Approach 2 to handle NAs:  Fill all the NAs with the previous or next value. (Hint: Using `fill` function).  Save the dataset after filling as a different data. The original data is unchanged (still have NAs). 

```{r}
dft4 = dft2 %>% 
  fill(names(dft2), .direction = 'updown')
str(dft4)
```
8. Approach 3 to handle NAs: For numeric variable, replace the NAs by the median.  For categorical variables, replace the NAs to the majority. 

```{r}

median_age <- median(dft2$age, na.rm=TRUE)
dft2$age <- replace_na(dft2$age, median_age)
majority_workclass <- names(which.max(table(dft2$workclass)))
dft2$workclass <- replace_na(dft2$workclass, majority_workclass)
median_fnlwgt <- median(dft2$fnlwgt, na.rm=TRUE)
dft2$fnlwgt <- replace_na(dft2$fnlwgt, median_fnlwgt)
majority_education <- names(which.max(table(dft2$education)))
dft2$education <- replace_na(dft2$education, majority_education)
majority_education.num <- names(which.max(table(dft2$education.num)))
dft2$education.num <- replace_na(dft2$education.num, majority_education.num)
majority_marital.status <- names(which.max(table(dft2$marital.status)))
dft2$marital.status <- replace_na(dft2$marital.status, majority_marital.status)
majority_occupation <- names(which.max(table(dft2$occupation)))
dft2$occupation <- replace_na(dft2$occupation, majority_occupation)
majority_relationship <- names(which.max(table(dft2$relationship)))
dft2$relationship <- replace_na(dft2$relationship, majority_relationship)
majority_race <- names(which.max(table(dft2$race)))
dft2$race <- replace_na(dft2$race, majority_race)
majority_sex <- names(which.max(table(dft2$sex)))
dft2$sex <- replace_na(dft2$sex, majority_sex)
median_capital.gain <- median(dft2$capital.gain, na.rm=TRUE)
dft2$capital.gain <- replace_na(dft2$capital.gain, median_capital.gain)
median_capital.loss <- median(dft2$capital.loss, na.rm=TRUE)
dft2$capital.loss <- replace_na(dft2$capital.loss, median_capital.loss)
median_hours.per.week <- median(dft2$hours.per.week, na.rm=TRUE)
dft2$hours.per.week <- replace_na(dft2$hours.per.week, median_hours.per.week)
majority_native.country <- names(which.max(table(dft2$native.country)))
dft2$native.country <- replace_na(dft2$native.country, majority_native.country)
majority_income <- names(which.max(table(dft2$income)))
dft2$income <- replace_na(dft2$income, majority_income)

```

```{r}
dft2
```

