
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 7: Visualization - Some aspects of ggplot2"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment7.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

-------

Use the data of your own.  Produce the following types of plots and comment on each plot. Plots should be meaningful. If you use the data we used in class, make sure the plots are not the same as the ones in the slides. All plots should have title, caption, appropriate labels on x and y-axis. 
```{r}
library(tidyverse)
library(knitr)
library(ggplot2)
df <- read_csv('https://bryantstats.github.io/math421/data/titanic.csv')
```

-------

1. Make a plot using `facet_wrap` by one categorical variable (`facet_wrap(~variable1)`)
```{r}
df %>% ggplot()+ 
  geom_point(mapping=aes(x=Sex, y=Fare))+
  facet_wrap(~Survived) +
  labs(x='Gender on the Titanic', 
       y = 'Average Fare Price',
       title = 'Average Fare of Passenger by Survival Rate and Gender', 
       caption = 'The higher the fare, the more likely to survive.')
```
This plot splits the people who survived and the people who did not survive, shows them side by side, and in each one it shows how much their ticket cost and what their gender is.

2. Make a plot using `facet_wrap` by two categorical variables (`facet_wrap(~variable1+variable2)`)

```{r}
df %>% ggplot()+ 
  geom_point(mapping=aes(x=Sex, y=Fare))+
  facet_wrap(~Survived + Pclass) +
  labs(x='Gender on the Titanic', 
       y = 'Average Fare Price',  
       title = 'Average Fare of Passenger by Survival Rate, Class, and Gender', 
       caption = 'The higher the class, the more likely to survive. Also, more men died compared to women by looking at the plot')
```
This plot splits the people who survived and the people who did not survive,and splits them by class as well. It shows this side by side, and in each one it shows how much their ticket cost and what their gender is.

3. Make a plot using `position ='dodge'`.

```{r}
df$Pclass = factor(df$Pclass)
df$Survived = factor(df$Survived)
df %>% ggplot()+ 
  geom_bar(mapping=aes(x=Pclass, fill=Survived), 
           position = 'dodge') +
  labs(x='Class on the Titanic', 
       y = 'Count of Passengers',  
       title = 'Deaths on Titanic based on Class', 
       caption = 'The lower the class, the more passengers that passed away.')
```
This plot shows how many people died on the titanic based on their class.

4. Make a plot using `position ='fill'`. 

```{r}
df$Pclass = factor(df$Pclass)
df$Survived = factor(df$Survived)
df %>% ggplot()+ 
  geom_bar(mapping=aes(x=Pclass, fill=Survived), 
           position = 'fill') +
  labs(x='Class on the Titanic', 
       y = 'Count of Passengers',  
       title = 'Deaths on Titanic based on Class', 
       caption = 'The lower the class, the more passengers that passed away.')
```
This plot shows how many people died on the titanic based on their class. I believe it is easier to see on this graph compared to the previous one that the lower the class the more passengers that passed away.

5. Make a plot using `geom_col`.

```{r}
df %>% group_by(Survived) %>% 
  summarise(average_age=mean(Age, na.rm=TRUE)) %>% 
  ggplot()+ 
  geom_col(mapping=aes(x=Survived, y=average_age))+
  labs(x='Survived/Not Survived', 
       y = 'Average Age',  
       title = 'Average Age of Survived/Not Survived on the Titanic', 
       caption = 'Average age for those who survived is younger than for those who did not.')
```
This plot shows the average age of passengers who died and passengers who lived that were on the titanic.

6. Change the theme of one of your plots. 
Problem 4 plot
```{r}
df$Pclass = factor(df$Pclass)
df$Survived = factor(df$Survived)
df %>% ggplot()+ 
  geom_bar(mapping=aes(x=Pclass, fill=Survived), 
           position = 'fill') +
  labs(x='Class on the Titanic', 
       y = 'Count of Passengers',  
       title = 'Deaths on Titanic based on Class', 
       caption = 'The lower the class, the more passengers that passed away.')+
  theme_dark()
```
This is the same plot used in problem 4; however, I used the dark theme with it instead of the regular theme.

7. Make a plot using combo filter + ggplot

```{r}
df %>% 
    filter(Age<=18, Pclass == 1) %>% 
    ggplot()+
    geom_bar(mapping=aes(x=Sex, fill=Survived))+
  labs(x='Gender on the Titanic', 
       y = 'Count of Passengers',  
       title = 'Deaths on Titanic based on Age and Gender', 
       caption = 'There were more females under 18 on the titanic than males that were in first class.')
```
This shows passengers under the age of 18 in first class that survived or did not survive the titanic.

8. Make a plot using combo group_by + summarise + geom_col

```{r}
df %>% 
  group_by(Pclass, Sex) %>% 
  summarise(mean_fare = Fare) %>% 
  ggplot()+
  geom_col(aes(x=Sex, y=mean_fare, fill=Pclass), position = 'fill')+
  labs(x='Gender on the Titanic', 
       y = 'Average Fare',  
       title = 'Average Fare on Titanic based on Class and Gender', 
       caption = 'First Class clearly bought more expensive tickets than the other classes; however, this could be becuase of outliers.')
```
This graph shows the average fare of passengers on titanic based on their class and gender

9. Save a plot and put a link of the plot to your Github Webpage.  To link a plot `abc.png` you just need to insert the following on the README.md

```{r, eval=FALSE}
[Link to the plot](abc.png)
```


```{r}
gg <- df %>% 
  group_by(Pclass, Sex) %>% 
  summarise(mean_fare = Fare) %>% 
  ggplot()+
  geom_col(aes(x=Sex, y=mean_fare, fill=Pclass), position = 'fill')+
  labs(x='Gender on the Titanic', 
       y = 'Average Fare',  
       title = 'Average Fare on Titanic based on Class and Gender', 
       caption = 'First Class clearly bought more expensive tickets than the other classes; however, this could be becuase of outliers.')

ggsave(filename = 'abc.png', plot = gg)
```


10. In this question, we will use  the Covid19 vaccination data for the US. The data and data dictionary can be found at the below link:

- [Data](https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations-by-manufacturer.csv)

- [Alternative Link](https://bryantstats.github.io/math421/data/vaccinations-by-manufacturer.csv)

```{r}
library(tidyverse)
df <- read_csv('https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations-by-manufacturer.csv')
```



`Geom_point` makes scatter plots, which plot two numeric (or Date) variables. A third categorical variable is often brought in for color. For example, we can compare different vaccine types used in the US by

```{r}
df %>% 
  filter(location=='United States') %>% 
  ggplot()+
  geom_point(mapping = aes(x = date, 
                                    y = total_vaccinations, 
                                    color = vaccine))
```

Do the follows. 

  - Use `geom_point` to compare the vaccines used by date in Argentina in 2022. 
  
  - Change `geom_point` to `geom_line` in the above codes to have the corresponding line plots. 

11. (Using the same dataset as in 10.) Sometime we need to do some calculations on the data before plotting. For example, the below codes is to compare the total vaccines (including all types of vaccines) by date between the US and the EU

```{r}
# the total vaccines (including all types of vaccines) by date
d1 <- df %>% 
  filter(location %in% c('United States', 'European Union')) %>% 
  group_by(date, location) %>% 
  summarise(total_vac2=sum(total_vaccinations, na.rm=TRUE))

# Plot
d1 %>% 
  ggplot()+
  geom_point(mapping=aes(x=date, 
                         y=total_vac2, 
                         color=location))
```

Notice that the above codes could be piped in one 

```{r, eval=FALSE}
df %>% 
  filter(location %in% c('United States', 'European Union')) %>% 
  group_by(date, location) %>% 
  summarise(total_vac2=sum(total_vaccinations, na.rm=TRUE)) %>% 
  ggplot()+
  geom_point(mapping=aes(x=date, 
                         y=total_vac2, 
                         color=location))
```


Do the follows. 

- Use `geom_point` compare the total vaccines (including all types of vaccines) by date between countries/regions in Asia

- Use `geom_point` compare the total vaccines (including all types of vaccines) by date between countries/regions in South America in 2021

