
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 6: Visualization - Aesthetic Mapping"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment6.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

### Questions on Your Selected Data

Choose a dataset and produce the following types of plots and comment on each plot. Plots should be meaningful. If you use the data we used in class, make sure the plots are not the same as the ones in the slides. 
```{r}
library(tidyverse)
library(ggplot2)
df <- read_csv('https://bryantstats.github.io/math421/data/titanic.csv')
```
-------

1. For one continuous variable:

- Density

```{r}
df %>% ggplot()+
  geom_density(mapping = aes(x = Fare))
```
This plot shows the fares and how the majority cost between 0-50 dollars. Skewed right.
- Histogram 

```{r}
df %>% ggplot()+
  geom_histogram(mapping = aes(x = Fare))
```

This plot shows the fares and how the majority cost between 0-50 dollars. Similar to the denisty one, it is skewed right.

- Boxplot

```{r}
df %>% ggplot()+
  geom_bar(mapping = aes(x = Sex))
```
Boxplot shows that the majority sex was male on the titanic

2. For one categorical variable

- Barplot

```{r}
df$Pclass = factor(df$Pclass)
df %>% ggplot() +
  geom_bar(mapping = aes(x = Pclass)) 
```
This shows the embarked on a one categorical barplot. The bars look the same because there isn't a second categorical variable to show with it. 
-------

3. For two continuous variables

- Scatter Plot

```{r}
df %>% ggplot()+geom_point(aes(x=Age, y=Parch))
```
This shows a scatter plot of how many siblings each person had on board with their age, and it almost looks like it is normally distributed.

- Line Plot

```{r}
df %>% ggplot()+geom_line(aes(x=Age, y=Parch))
```
Used the same variable for the line plot and you can see the normal distribution more clearly here

- Smooth Plot

```{r}
df %>% ggplot()+geom_smooth(aes(x=Age, y=Parch))
```
This graph also would make sense if the relation between parch and age is normally distributed

-------

4. For one continuous + one categorical variables

- Density

```{r}
df %>% ggplot()+
  geom_density(mapping = aes(x = Fare, color = Sex))
```
This graph shows the fare in relation with the gender. In a way, it also reveals how many more men were on the titanic compared to women without meaning to.

- BoxPlot

```{r}
df %>% ggplot()+
  geom_boxplot(mapping = aes(x = Fare, y = Sex))
```
Once again shows relation with the gender and the fare. It reveals that the median fare for women is greater than for men, probably because there were more men on the titanic so more men bought cheaper tickets. 
-------

5. For two categorical variables: barplot

```{r}
df$Pclass = factor(df$Pclass)
df$Survived = factor(df$Survived)
df %>% ggplot()+
  geom_bar(mapping=aes(x=Pclass, fill=Survived), position = 'fill')
```
This is comparing class against who survived and who didn't. Not sure why no color is showing up.  
-------

6. A plot that contains three variables

```{r}
df %>% ggplot() + geom_point(aes(x=Age, y=Fare, color = Pclass))

```
This shows the age of people and how much their fare cost. The color shows the class they were in. You can see how the higher the fare was the darker the color gets (which means the higher the class is)
